\documentclass[]{deedy-resume-openfont}

\begin{document}

\lastupdated

\namesection{Aleksandre}{Khvadagadze}{
\href{mailto:skhvadagadze@gmail.com}{skhvadagadze@gmail.com} | (314) 940-5601 \\
LinkedIn: \href{https://www.linkedin.com/in/aleksandre-khvadagadze-0a4518325/}{aleksandre-khvadagadze} \\
GitHub: \href{https://github.com/Phlabry}{Phlabry}
}

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
Junior CS student looking to gain \\
experience in the industry through \\
internships.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\subsection{Saint Louis University}
\descript{B.S. in Computer Science}
\location{May 2027 | St. Louis, MO}
\location{GPA: 3.58 / 4.0}
Dean’s List — Fall 2024
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
Data Structures \\
Algorithms \\
Web Technologies \\
Computer Organization and Systems \\
Principles of Computing Systems \\
Object-Oriented Software Design \\
Discrete Mathematics
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}

\subsection{Programming}
C++ \textbullet{} Python \textbullet{} JavaScript \\
HTML \textbullet{} CSS
\sectionsep

\subsection{Frontend}
React.js \textbullet{} TailwindCSS \\
Framer Motion
\sectionsep

\subsection{Backend}
Node.js \textbullet{} Express \\
Flask \textbullet{} REST APIs
\sectionsep

\subsection{Tools}
Linux \textbullet{} Git \textbullet{} GitHub \\
Docker (Basics) \textbullet{} Postman \\
Vite \textbullet{} Bash
\sectionsep

\subsection{Data}
PostgreSQL \textbullet{} Pandas \\
JSON APIs \textbullet{} SQL
\sectionsep

\subsection{Languages}
Georgian (Native) \\
English (C2) \\
Russian (Beginner)
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS & HACKATHONS (ANCHOR)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects \& Hackathons}

\runsubsection{HackSLU Hackathon}
\descript{| Social Impact Winner}
\location{Mar 2025 | St. Louis, MO}
\vspace{\topsep}
\begin{tightemize}
\item Built a playable Love2D prototype in 24 hours (Lua).
\item Won 1st place in the Social Impact category.
\item Chose Love2D for lightweight runtime and fast iteration.
\item Iterated gameplay/UX versions to validate core mechanics.
\item Shared ownership across logic, UI, and state handling.
\end{tightemize}
\sectionsep

\runsubsection{Washington University Hackathon}
\descript{| Finalist — FlavorAI}
\location{Apr 2025 | St. Louis, MO}
\vspace{\topsep}
\begin{tightemize}
\item Built an AI restaurant recommendation prototype in 36 hours.
\item Generated taste profiles using Google Gemini API.
\item Integrated Google Maps API for nearby restaurant discovery.
\item Shipped demo using Flask, React, Python, and Pandas.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{SkyInsights}
\descript{| Co-Founder / Developer}
\location{Jan 2025 – Present | Tbilisi, Georgia}
\vspace{\topsep}
\begin{tightemize}
\item Built and launched an AI-powered startup platform demo.
\item Onboarded 30+ early test users.
\item Collected feedback from 10–15 users and iterated UX/features.
\item Worked in a 3-person team with shared full-stack ownership.
\item Integrated AI-driven analysis to generate structured insights.
\item Paused active dev during peak university semester load.
\end{tightemize}
\sectionsep

\runsubsection{Georgian Water and Power (GWP)}
\descript{| Software / IT Intern}
\location{Jun 2025 – Jul 2025 | Tbilisi, Georgia}
\vspace{\topsep}
\begin{tightemize}
\item Rotated through IT support, ERP, and software teams.
\item Assisted cross-department enterprise workflow coordination.
\item Supported system integration tasks across admin/ERP systems.
\item Prepared for dev tasks using Angular and dotenv-based backends.
\end{tightemize}
\sectionsep

\runsubsection{IT Step Academy Georgia}
\descript{| Team Lead}
\location{May 2019 – Sep 2019 | Tbilisi, Georgia}
\vspace{\topsep}
\begin{tightemize}
\item Designed programming exercises to teach core fundamentals.
\item Mentored beginner programmers through guided practice.
\item Coordinated tasks and provided technical direction.
\end{tightemize}
\sectionsep

\runsubsection{Saint Louis University Athletics Department}
\descript{| ESPN+ \& Billiken Media Relations Student Assistant}
\location{May 2025 – Present | St. Louis, MO}
\vspace{\topsep}
\begin{tightemize}
\item Assist in live graphics production for ESPN+ broadcasts.
\item Support fast-paced live production under time constraints.
\end{tightemize}
\sectionsep


\end{minipage}
\end{document}
